### 2013-09-28 manuscripts/dpp-msbayes/dpp-msbayes.tex
Working on results of dpp ms.
Also adding table of models used to generated datasets for
power analyses.

\subsubsection*{Obtaining an approximate posterior from the prior samples}
We use a rejection algorithm to retain an approximate posterior sample of
\paramSampleVector{} from the prior sample
$\paramSampleMatrix = (\paramSampleVector{1}, \ldots, \paramSampleVector{\numPriorSamples})$.
First, the observed summary statistics \ssVectorObs, and the summary statistics
of the prior samples 
$\ssMatrix = (\ssVector{1}, \ldots, \ssVector{\numPriorSamples})$,
are standardized using the means and standard deviations of the statistics from
the prior sample (i.e., the prior mean is subtracted from each statistic, and then
it is divided by the prior standard deviation).
After all statistics are standardized, the Euclidean distance between
the \ssVectorObs and each \ssVector{} within \ssMatrix is calculated.
The samples that fall within a range of tolerance \tol around \ssVectorObs
are retained.
The range of tolerance is determined by specifying the number of desired
posterior samples to be retained.
Post-hoc adjustment of the posterior sample can also be performed with a number
of regression techniques \citep{Beaumont2002,Blum2009,Leuenberger2010}.
For our analyses, we use the general linear model (GLM) regression adjustment
\citet{Leuenberger2010}, which \citet{Oaks2012} showed performed very
similarly to weighted local-linear regression and multinomial logistic
regression adjustments \citep{Beaumont2002} for \msb posteriors.

@@

\subsection*{Assessing power}
We evaluated the power of the same four models (Table~\ref{tabPriors}) to
detect random variation in divergence times using methods similar to
\citet{Oaks2012}.
For all of our power simulations, we used a simulated data structure identical
to that of the empirical dataset of Philippine vertebrates analyzed by
\citet{Oaks2012}, which consists of 22 pairs of populations.
For each of the four models, we generated $2\e6$ samples from the prior.
We then generated pseudo-observed datasets from three series of models.
One series of models, which we denote \powerSeriesOld, is identically
distributed as \modelOld except that the divergence times for each of the 22
pairs of populations are randomly drawn from a series of uniform distributions,
$U(0, \divt{max})$, where \divt{max} was set to: 0.2, 0.4, 0.6, 0.8, 1.0, and
2.0, in \globalcoalunit generations.
A second series of models, \powerSeriesUniform, are identically distributed as
\modelUniform except that the 22 divergence times are randomly drawn from the
same series of uniform priors as above.
The third series of models, \powerSeriesUniformExp, is also identically
distributed as \modelUniform except that the 22 divergence times are randomly
drawn from a series of of exponential distributions: $Exp(17.3205)$,
$Exp(8.6603)$, $Exp(5.7735)$, $Exp(4.33013)$, $Exp(3.4641)$, and $Exp(1.7321)$.
These exponential distributions have the same variance as their uniform
counterparts in the first two series of models.

@@

\section*{Results}

@@

@@

%% Power accuracy results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniformExp}{\modelDPP}
}{figPowerAccuracyUniformExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniformExp}{\modelUniform}
}{figPowerAccuracyUniformExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniformExp}{\modelOld}
}{figPowerAccuracyUniformExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesUniformExp}{\modelUshaped}
}{figPowerAccuracyUniformExpUshaped}

@@

%% Power psi results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniformExp}{\modelDPP}
}{figPowerPsiUniformExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniformExp}{\modelUniform}
}{figPowerPsiUniformExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniformExp}{\modelOld}
}{figPowerPsiUniformExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesUniformExp}{\modelUshaped}
}{figPowerPsiUniformExpUshaped}

@@

%% Power dispersion results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniformExp}{\modelDPP}
}{figPowerDispersionUniformExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniformExp}{\modelUniform}
}{figPowerDispersionUniformExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniformExp}{\modelOld}
}{figPowerDispersionUniformExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesUniformExp}{\modelUshaped}
}{figPowerDispersionUniformExpUshaped}

@@

%% Power psi probability results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniformExp}{\modelDPP}
}{figPowerPsiProbUniformExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniformExp}{\modelUniform}
}{figPowerPsiProbUniformExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniformExp}{\modelOld}
}{figPowerPsiProbUniformExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesUniformExp}{\modelUshaped}
}{figPowerPsiProbUniformExpUshaped}

@@

%% Power dispersion prob results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniformExp}{\modelDPP}
}{figPowerDispersionProbUniformExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniformExp}{\modelUniform}
}{figPowerDispersionProbUniformExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniformExp}{\modelOld}
}{figPowerDispersionProbUniformExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesUniformExp}{\modelUshaped}
}{figPowerDispersionProbUniformExpUshaped}

>>>>

\subsubsection*{Obtaining an approximate posterior from the prior samples}
We use a rejection algorithm to retain an approximate posterior sample of
\paramSampleVector{} from the prior sample
$\paramSampleMatrix = (\paramSampleVector{1}, \ldots, \paramSampleVector{\numPriorSamples})$.
First, the observed summary statistics \ssVectorObs, and the summary statistics
of the prior samples 
$\ssMatrix = (\ssVector{1}, \ldots, \ssVector{\numPriorSamples})$,
are standardized using the means and standard deviations of the statistics from
the prior sample (i.e., the prior mean is subtracted from each statistic, and then
it is divided by the prior standard deviation).
After all statistics are standardized, the Euclidean distance between
the \ssVectorObs and each \ssVector{} within \ssMatrix is calculated.
The samples that fall within a range of tolerance \tol around \ssVectorObs
are retained.
The range of tolerance is determined by specifying the number of desired
posterior samples to be retained.
Post-hoc adjustment of the posterior sample can also be performed with a number
of regression techniques \citep{Beaumont2002,Blum2009,Leuenberger2010}.
For our analyses, we use the general linear model (GLM) regression adjustment
\citet{Leuenberger2010} as implemented in \abctoolbox
\citep[v1.1;][]{ABCtoolbox}, which \citet{Oaks2012} showed performed very
similarly to weighted local-linear regression and multinomial logistic
regression adjustments \citep{Beaumont2002} for \msb posteriors.

@@

\subsection*{Assessing power}
We evaluated the power of the same four models (Table~\ref{tabPriors}) to
detect random variation in divergence times using methods similar to
\citet{Oaks2012}.
For all of our power simulations, we used a simulated data structure identical
to that of the empirical dataset of Philippine vertebrates analyzed by
\citet{Oaks2012}, which consists of 22 pairs of populations.
For each of the four models, we generated $2\e6$ samples from the prior.
We then generated pseudo-observed datasets from three series of models.
One series of models, which we denote \powerSeriesOld, is identically
distributed as \modelOld except that the divergence times for each of the 22
pairs of populations are randomly drawn from a series of uniform distributions,
$U(0, \divt{max})$, where \divt{max} was set to: 0.2, 0.4, 0.6, 0.8, 1.0, and
2.0, in \globalcoalunit generations.
A second series of models, \powerSeriesUniform, are identically distributed as
\modelUniform except that the 22 divergence times are randomly drawn from the
same series of uniform priors as above.
The third series of models, \powerSeriesExp, is also identically
distributed as \modelUniform except that the 22 divergence times are randomly
drawn from a series of of exponential distributions: $Exp(17.3205)$,
$Exp(8.6603)$, $Exp(5.7735)$, $Exp(4.33013)$, $Exp(3.4641)$, and $Exp(1.7321)$.
These exponential distributions have the same variance as their uniform
counterparts in the first two series of models.

@@

\section*{Results}
\subsection*{Validation analyses: Estimation accuracy}
In terms of estimating summary statistics of model parameters (\divTimeNum,
\divTimeDispersion, and \divTimeMean), the \modelDPP performs similarly when
applied to datasets generated under all four models of Table \ref{tabPriors}
(Figs.\
\labelcref{figValidationAccuracyDPPDPP,figValidationAccuracyUniformDPP,figValidationAccuracyOldDPP,figValidationAccuracyUshapedDPP}).
The same is true for models \modelUniform (Figs.\
\labelcref{figValidationAccuracyDPPUniform,figValidationAccuracyUniformUniform,figValidationAccuracyOldUniform,figValidationAccuracyUshapedUniform})
and \modelUshaped (Figs.\
\labelcref{figValidationAccuracyDPPUshaped,figValidationAccuracyUniformUshaped,figValidationAccuracyOldUshaped,figValidationAccuracyUshapedUshaped}).
All three of the models with exponential priors on nuisance parameters
(\modelDPP, \modelUniform, and \modelUshaped) perform well when applied
to the data generated under the original \msb model, \modelOld (Figs.\
\labelcref{figValidationAccuracyOldDPP,figValidationAccuracyOldUniform,figValidationAccuracyOldUshaped}).
The \modelOld model also performed well on its own datasets (Figure
\ref{figValidationAccuracyOldOld}), but performed poorly when applied to the
data generated under the other three models (Figs.\
\labelcref{figValidationAccuracyDPPOld,figValidationAccuracyUniformOld,figValidationAccuracyUshapedOld}).
Thus, the newly implemented models display greater robustness than
the original model.

Posterior adjustment with GLM regression does improve the estimation
accuracy for the continuous variables \divTimeDispersion and \divTimeMean,
however, this is not always true for estimating the discrete variable
\divTimeNum (Figs.\
\labelcref{figValidationAccuracyDPPDPP,figValidationAccuracyUniformDPP,figValidationAccuracyOldDPP,figValidationAccuracyUshapedDPP,figValidationAccuracyDPPUniform,figValidationAccuracyUniformUniform,figValidationAccuracyOldUniform,figValidationAccuracyUshapedUniform,figValidationAccuracyDPPUshaped,figValidationAccuracyUniformUshaped,figValidationAccuracyOldUshaped,figValidationAccuracyUshapedUshaped,figValidationAccuracyDPPOld,figValidationAccuracyUniformOld,figValidationAccuracyUshapedOld,figValidationAccuracyOldOld}).

\subsection*{Validation analyses: Model-choice accuracy}
The \msb model, and our modifications of it, is a model-choice method
with the primary purpose of estimating the probabilities of models
of divergence across taxa.
Thus, it is critical to assess the method's ability to accurately
estimate the posterior probabilities of divergence models.
Our results demonstrate that the unadjusted estimates of
divergence models are generally more accurate than the regression
adjusted estimates, especially when using $\divTimeDispersion < 0.01$
to assess the probability of the one divergence model (Figs.\
\labelcref{figValidationModelChoiceDPPDPP,figValidationModelChoiceUniformDPP,figValidationModelChoiceOldDPP,figValidationModelChoiceUshapedDPP,figValidationModelChoiceDPPUniform,figValidationModelChoiceUniformUniform,figValidationModelChoiceOldUniform,figValidationModelChoiceUshapedUniform,figValidationModelChoiceDPPUshaped,figValidationModelChoiceUniformUshaped,figValidationModelChoiceOldUshaped,figValidationModelChoiceUshapedUshaped,figValidationModelChoiceDPPOld,figValidationModelChoiceUniformOld,figValidationModelChoiceUshapedOld,figValidationModelChoiceOldOld}).
Thus, we will focus our discussion of the results on the unadjusted estimates.

The model-choice behavior of the \modelDPP is relatively accurate when applied
to datasets generated under models \modelDPP, \modelUniform, and \modelOld
(Figs.\
\labelcref{figValidationModelChoiceDPPDPP,figValidationModelChoiceUniformDPP,figValidationModelChoiceOldDPP}).
It is less accurate and tends to underestimate the probability of the
one-divergence model when applied to the data generated under \modelUshaped
(Figure \ref{figValidationModelChoiceUshapedDPP}).
The \modelUniform model performs almost identically as \modelDPP in
terms of model-choice accuracy (Figs.\
\labelcref{figValidationModelChoiceDPPUniform,figValidationModelChoiceUniformUniform,figValidationModelChoiceOldUniform,figValidationModelChoiceUshapedUniform}).

@@

\begin{table}[htbp]
    \sffamily
    % \footnotesize
    % \addtolength{\tabcolsep}{-0.08cm}
    \rowcolors{2}{}{myGray}
    %\captionsetup{font=footnotesize}
    \caption{The models we used to simulate pseudo-replicate datasets for
        assessing the power of the models in Table \ref{tabPriors}.}
    \centering
    \begin{tabular}{ l l l l l }
        \toprule
        & \multicolumn{4}{c}{Priors} \\
        \cmidrule(){2-5}
        Model series & \divTimeIndexVector & \divTime{} & \ancestralTheta{} & \descendantTheta{}{} \\
        \midrule
            \powerSeriesOld & $\divTimeNum = 22$
                            & $\divTime{} \sim U(0,0.2)$
                            & $\ancestralTheta{} \sim U(0, 0.05)$
                            & $\descendantThetaMean{} \sim U(0, 0.05)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim U(0,0.4)$
                            & $\ancestralTheta{} \sim U(0, 0.05)$
                            & $\descendantThetaMean{} \sim U(0, 0.05)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim U(0,0.6)$
                            & $\ancestralTheta{} \sim U(0, 0.05)$
                            & $\descendantThetaMean{} \sim U(0, 0.05)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim U(0,0.8)$
                            & $\ancestralTheta{} \sim U(0, 0.05)$
                            & $\descendantThetaMean{} \sim U(0, 0.05)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim U(0,1.0)$
                            & $\ancestralTheta{} \sim U(0, 0.05)$
                            & $\descendantThetaMean{} \sim U(0, 0.05)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim U(0,2.0)$
                            & $\ancestralTheta{} \sim U(0, 0.05)$
                            & $\descendantThetaMean{} \sim U(0, 0.05)$ \\
        \midrule
            \powerSeriesUniform & $\divTimeNum = 22$
                            & $\divTime{} \sim U(0,0.2)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim U(0,0.4)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim U(0,0.6)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim U(0,0.8)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim U(0,1.0)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim U(0,2.0)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\
        \midrule
            \powerSeriesExp & $\divTimeNum = 22$
                            & $\divTime{} \sim Exp(17.3205)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim Exp(8.6603)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim Exp(5.7735)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim Exp(4.3301)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim Exp(3.4641)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\
                            & $\divTimeNum = 22$
                            & $\divTime{} \sim Exp(1.7321)$
                            & $\ancestralTheta{} \sim Exp(40)$
                            & $\descendantTheta{}{} \sim Exp(40)$ \\
        \bottomrule
    \end{tabular}
    \label{tabPowerModels}
\end{table}

@@

%% Power accuracy results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesExp}{\modelDPP}
}{figPowerAccuracyExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesExp}{\modelUniform}
}{figPowerAccuracyExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesExp}{\modelOld}
}{figPowerAccuracyExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_accuracy_omega_median.pdf}{
    \powerAccuracyCaption{\powerSeriesExp}{\modelUshaped}
}{figPowerAccuracyExpUshaped}

@@

%% Power psi results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesExp}{\modelDPP}
}{figPowerPsiExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesExp}{\modelUniform}
}{figPowerPsiExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesExp}{\modelOld}
}{figPowerPsiExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_psi_mode.pdf}{
    \powerPsiCaption{\powerSeriesExp}{\modelUshaped}
}{figPowerPsiExpUshaped}

@@

%% Power dispersion results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesExp}{\modelDPP}
}{figPowerDispersionExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesExp}{\modelUniform}
}{figPowerDispersionExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesExp}{\modelOld}
}{figPowerDispersionExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_omega_median.pdf}{
    \powerDispersionCaption{\powerSeriesExp}{\modelUshaped}
}{figPowerDispersionExpUshaped}

@@

%% Power psi probability results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesExp}{\modelDPP}
}{figPowerPsiProbExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesExp}{\modelUniform}
}{figPowerPsiProbExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesExp}{\modelOld}
}{figPowerPsiProbExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_psi_prob.pdf}{
    \powerPsiProbCaption{\powerSeriesExp}{\modelUshaped}
}{figPowerPsiProbExpUshaped}

@@

%% Power dispersion prob results
\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_dpp_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesExp}{\modelDPP}
}{figPowerDispersionProbExpDPP}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_uniform_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesExp}{\modelUniform}
}{figPowerDispersionProbExpUniform}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_old_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesExp}{\modelOld}
}{figPowerDispersionProbExpOld}

\mFigure{../../power-comparison/results/pymsbayes-results/plots/exp_u-shaped_power_omega_prob.pdf}{
    \powerDispersionProbCaption{\powerSeriesExp}{\modelUshaped}
}{figPowerDispersionProbExpUshaped}
